Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2018-05-11 manuscript.tex
Rewording the introduction

% utilizing the combo of small satellite and low thrust propulsion offers new mission scenarios 
Recent developments in miniature electric propulsion and small satellites now offer the potential for new research oppportunities~\cite{folta2015,haque2013}.
The potential for more demanding missions places an even greater importance on the mission design to ensure that optimal trajectories satisfy mission requirements~\cite{folta2015,koon2011,ross2006,gomez2001}. 
Optimally combining the structure of the dynamic environment with low-thrust propulsion systems is vital for future mission success.

>>>>

% utilizing the combo of small satellite and low thrust propulsion offers new mission scenarios 
Recent developments in miniature electric propulsion and small satellites now offer the potential of new research oppportunities~\cite{folta2015,haque2013}.
The potential for more demanding missions places an even greater importance on the mission design to ensure that optimal trajectories satisfy mission requirements~\cite{folta2015,koon2011,ross2006,gomez2001}. 
Optimally combining the structure of the dynamic environment with low-thrust propulsion systems is vital for future mission success.
